---
title: '**Visualisation**: Assignment 1'
author: 'Name: Adarsha Mondal | Roll Number: MDS202205'
date: 'Dead Line : 03 Oct 2022'
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(gridExtra)
library(reshape2)
library(ggpubr)
library(formatR)
theme_set(theme_bw())
```

## Instruction:

1)  Work on the \`Assignment1.Rmd' file. Compile the file as pdf. Submit only the pdf file in moodle.
2)  Make sure you write your name and roll number at the top of the \`Assignment1.Rmd' file.

## Total Marks: 10 points

## Problem 1 (3 points)

**Problem Statement:** Write an $\texttt{R}$ function which will test Central Limit Theorem.

-   Assume the underlying population distribution follow Poisson distribution with rate parameter $\lambda$
-   We want to estimate the unknown $\lambda$ with the sample mean $$\hat{\lambda}=\frac{1}{n}\sum_{i=1}^{n}X_i$$
-   The exact sampling distribution of $\hat{\lambda}$ is unknown
-   But CLT tells us that as sample size $n$ increases the sampling distribution of $\hat{\lambda}$ can be approximated by Gaussian distribution.

### **Input in the function:**

-   $n$: sample size
-   $\lambda$ : rate parameter
-   $N$: simulation size

## **Output from the function:**

-   Histogram of the sampling distribution using `ggplot`
-   QQ-plot using `ggplot`

## **Test cases:**

-   case 1 a: $\lambda =0.7$, n=10, N=5000

-   case 1 b: $\lambda=0.7$, n=30, N=5000

-   case 1 c: $\lambda=0.7$, n=100, N=5000

-   case 1 c: $\lambda=0.7$, n=300, N=5000

-   case 2 a: $\lambda=1.7$, n=10, N=5000

-   case 2 b: $\lambda=1.7$, n=30, N=5000

-   case 2 c: $\lambda=1.7$, n=100, N=5000

-   case 2 c: $\lambda=1.7$, n=300, N=5000

```{r tidy = TRUE, tidy.opts = list(width.cutoff = 50)}
cumulative_df = data.frame(means = numeric(0), 
                samp_size = character(0), lambda = character(0))

problem_1 = function(lambda, sample_size, sim_size){
  samplings_mean_vec = replicate(sim_size,mean(rpois(sample_size,lambda)))
  samplings_mean_df = data.frame(samplings_mean_vec, 
        rep(paste("Sample size :", sample_size,sep = " "),sim_size), 
        rep(paste("Lambda :",lambda,sep = " "),sim_size))
  return(samplings_mean_df)
}

lambdas = c(0.7, 1.7)

test_cases = c(010,030,100,300)

simulation_size = 5000

for (lambda in lambdas){
  for (test in test_cases){
    cumulative_df = rbind(cumulative_df, problem_1(lambda,test,simulation_size))
  }
}
colnames(cumulative_df) = c('means', 'samp_size', 'lambda')

# Histigrams
print(ggplot(cumulative_df)+aes(x=means)+
  geom_histogram(color="white", fill="black",bins=22)+
  geom_vline(xintercept = 0.7, linetype="dashed", color="orange",size=1)+
  geom_vline(xintercept = 1.7, linetype="dashed", color="blue",size=1)+
  #facet_wrap(~samp_size, ncol=4)+
  facet_grid(lambda ~ samp_size, scales = "free")+
  theme(axis.line = element_line(colour = "darkblue", size = 1, 
                                 linetype = "solid"), 
        axis.title.x = element_text(face="bold",size=15), 
        axis.title.y = element_text(face="bold",size=15))+
  geom_text(aes(0.6,2000,label = 0.7, hjust=-1))+
  geom_text(aes(1.6,2000,label = 1.7, hjust=-1))+
  labs(title = "Histograms corresponding to all test-cases",x = "Sample Means",
       y="Count"))

#head(cumulative_df[cumulative_df$lambda=='Lambda : 0.7',])
# Q-Q Plots
for (lambda in lambdas){
  
  df = cumulative_df[cumulative_df$lambda==paste('Lambda :',lambda,sep = ' '),]
  
  print(ggplot(data=df, aes(sample = means))+geom_qq(size=1)+
    geom_qq_line(color = "blue")+
    facet_wrap(vars(samp_size), scales = "free_y",nrow = 1)+
    theme(axis.line = element_line(colour = "darkblue", size = 1, 
                                   linetype = "solid"), 
          axis.title.x = element_text(face="bold",size=15), 
          axis.title.y = element_text(face="bold",size=15))+
    labs(title = paste('Q-Q Plots corresponding to Lambda =',lambda,sep = ' '),
         x = "Theoretical Quantiles", y = "Sample Quantiles"))
}
```


### **Problem 2:** (2 points)

Consider the `JohnsonJohnson` dataset. The datset contains the Quarterly earnings (dollars) per Johnson & Johnson share 1960--80.

a)  Draw the time series plot of Quarterly earnings in regular scale and log-scale using the `ggplot` (1 point)

```{r}
head(JohnsonJohnson)
```

```{r  tidy = TRUE, tidy.opts = list(width.cutoff = 50)}
problem_2 = function(){
  jj_earnings_df = data.frame(time = time(JohnsonJohnson), 
                              earnings = JohnsonJohnson)
  
  line = ggplot(data = jj_earnings_df, aes(x = time, y = earnings)) + 
    geom_line(color = "#00AFBB", size = 1)+
    geom_smooth()+
    theme(axis.line = element_line(colour = "black", size = 1, 
                                   linetype = "solid"), 
          axis.title.x = element_text(face="bold",size=12), 
          axis.title.y = element_text(face="bold",size=12))+
    labs(title = "Time Series plot",
         subtitle = "Quarterly earnings from 1960 - 1980",
         x = "Time", 
         y = "Earnings($)")
  
  log = ggplot(data = jj_earnings_df, aes(x = time, y = earnings)) + 
    geom_line(color = "red", size = 1) + scale_y_continuous(trans = "log")+
    geom_smooth(method = "lm")+
    theme(axis.line = element_line(colour = "black", size = 1, 
                                   linetype = "solid"), 
          axis.title.x = element_text(face="bold",size=12), 
          axis.title.y = element_text(face="bold",size=12))+
    labs(title = "Log-scaled Time Series plot",
         subtitle = "Quarterly earnings from 1960 - 1980",
         x = "Time", 
         y = "log(Earnings)")
  
  figure = ggarrange(line, log, ncol = 2)
  return(figure)
}
print(problem_2())
```


### **Problem 3:** (2 points)

-   An experiment was conducted to measure and compare the effectiveness of various feed supplements on the growth rate of chickens.

-   Following R-code is a standard side-by-side boxplot showing effect of feed supplements on the growth rate of chickens.

```{r,fig=T}
boxplot(weight~feed,data=chickwts,pch=20
        ,main = "chickwt data"
        ,ylab = "Weight at six weeks (gm)"
        ,xlab = "Feed Type")
```

a)  Reproduce the same plot using the `ggplot`; while fill each boxes with different colour.

b)  In addition draw probability density plot for weights of chicken's growth by each feed seperately using the `ggplot`. Draw this plot seperately.

```{r tidy = TRUE, tidy.opts = list(width.cutoff = 50)}
problem_3 = function(){
  chickwts_df = data.frame(chickwts)
  
  #
  print(ggplot(chickwts_df, aes(x = feed, y = weight, fill=feed))+
          aes(color = feed)+
          geom_boxplot(alpha=0.3)+
          theme(axis.line = element_line(colour = "black", size = 1, 
                                         linetype = "solid"), 
                axis.title.x = element_text(face="bold",size=15), 
                axis.title.y = element_text(face="bold",size=15),
                axis.text.x = element_text(face = "bold",size = 12),
                axis.text.y = element_text(face = "bold",size = 12)))
  
  # Probability densities
  print(ggplot(chickwts_df)+
          geom_density(aes(y=weight, fill="f8766d"))+
          facet_grid(~feed)+
          theme(axis.line = element_line(colour = "black", size = 1, 
                                         linetype = "solid"), 
                axis.title.x = element_text(face="bold",size=15), 
                axis.title.y = element_text(face="bold",size=15),
                axis.text.x = element_text(angle = -90,face = "bold",size = 10),
                axis.text.y = element_text(face = "bold",size = 10),
                legend.position="none") +
          
          labs(title = "Probability of weight of chicks depending on feed",
               x = "Probability Density", 
               y = "Weight(g)"))
}
problem_3()
```


### **Problem 4:** (3 points)

Consider the `EuStockMarkets` data available in `R`. Contains the daily closing prices of major European stock indices: Germany DAX (Ibis), Switzerland SMI, France CAC, and UK FTSE. The data are sampled in business time, i.e., weekends and holidays are omitted.

```{r}
head(EuStockMarkets)
```

-   Suppose $P_t$ is the closing price of a stock indices on day $t$.
-   The daily return $r_t$ is defined as $$
    r_t = \log(P_t)-\log(P_{t-1}).
    $$

a)  Draw time-series plot of $P_t$ for all four markets
b)  Draw time-series plot of $r_t$ for all four markets
c)  Draw histogram of $P_t$ for all four markets
d)  Draw histogram of $r_t$ for all four markets
e)  Suppose you invested \$ 1000 in each market indices on day 1. Plot how your investment grows on the same plot for all four markets. Make your plot using `ggplot`.
f)  Check which market outperform others during the same time?

Make all your plots using `ggplot`.

```{r tidy = TRUE, tidy.opts = list(width.cutoff = 50)}
time = data.frame(time = time(EuStockMarkets))
data = data.frame(EuStockMarkets)
n = nrow(data)

for(i in 1:4){
  temp_dr = c(0)
  temp_inv = c(1000)
  for(j in 2:n){
    k = log(data[j,i]/data[j-1,i])
    temp_dr = c(temp_dr,k)
    temp_inv = c(temp_inv,temp_inv[j-1]*exp(k))
  }

  if(i==1){
    dr_df = data.frame(IDX_dr = temp_dr)
    investment_df = data.frame(IDX_inv = temp_inv)
  }
  else{
    dr_df[paste(names(data)[i], 'dr', sep = '_')] = data.frame(temp_dr)
    investment_df[paste(names(data)[i], 'inv', sep = '_')] = data.frame(temp_inv)
  }
}

inv_melt=melt(cbind(time,investment_df),id=c('time'),value.name = "value")

pt_melt = melt(cbind(time, data), id = c("time"), value.name = "value")

dr_melt = melt(cbind(time, dr_df), id = c("time"), value.name = "value")
```

a)
```{r tidy = TRUE, tidy.opts = list(width.cutoff = 50)}
print(ggplot(pt_melt)+aes(x=time, y=value)+
  geom_line(aes(color=variable),size=1)+
  facet_grid(vars(variable))+
  labs(title = "Performance on closing value of various Indices(P_t)", 
       y = "Closing value")+
  theme(axis.line = element_line(colour = "black", size = 0.6, 
                                 linetype = "solid"), 
        axis.title.x = element_text(face="bold",size=15), 
        axis.title.y = element_text(face="bold",size=15),
        axis.text.x = element_text(face = "bold",size = 12),
        axis.text.y = element_text(face = "bold",size = 12),
        legend.position = "none"))
```

b)
```{r tidy = TRUE, tidy.opts = list(width.cutoff = 50)}
print(ggplot(dr_melt)+aes(x=time, y=value)+
  geom_line()+
  geom_point(alpha=0.3,aes(colour=value>0))+
  facet_grid(vars(variable))+
  labs(title = "Performance on daily return of various Indices(r_t)", 
       y = "log(ratio of consecutive day values)")+
  theme(axis.line = element_line(colour = "black", size = 0.6, 
                                 linetype = "solid"), 
        axis.title.x = element_text(face="bold",size=15), 
        axis.title.y = element_text(face="bold",size=15),
        axis.text.x = element_text(face = "bold",size = 12),
        axis.text.y = element_text(face = "bold",size = 12)))
```

c)
```{r tidy = TRUE, tidy.opts = list(width.cutoff = 50)}
print(ggplot(pt_melt)+aes(x=value)+
  geom_histogram(aes(color=variable),bins=50)+
  facet_grid(vars(variable))+
  labs(title = 
         "Deviation of closing value of various indices from its centrality", 
       y = "Count",x="Closing Value")+
  theme(axis.line = element_line(colour = "black", size = 0.6, 
                                 linetype = "solid"), 
        axis.title.x = element_text(face="bold",size=15), 
        axis.title.y = element_text(face="bold",size=15),
        axis.text.x = element_text(face = "bold",size = 12),
        axis.text.y = element_text(face = "bold",size = 12),
        legend.position = "none"))
```

d)
```{r tidy = TRUE, tidy.opts = list(width.cutoff = 50)}
print(ggplot(dr_melt)+aes(x=value)+
  geom_histogram(aes(color=variable),bins=40)+
  facet_grid(vars(variable))+
  geom_vline(xintercept = 0, linetype="dashed", color="orange",size=1)+
  labs(title = 
         "Count of daily return of various indices", 
       y = "Count",x="Daily return")+
  theme(axis.line = element_line(colour = "black", size = 0.6, 
                                 linetype = "solid"), 
        axis.title.x = element_text(face="bold",size=15), 
        axis.title.y = element_text(face="bold",size=15),
        axis.text.x = element_text(face = "bold",size = 12),
        axis.text.y = element_text(face = "bold",size = 12),
        legend.position = "none"))
```

e)
```{r tidy = TRUE, tidy.opts = list(width.cutoff = 50)}
print(ggplot(inv_melt, aes(x = time, y = value)) + 
  geom_line(aes(color = variable, linetype = "solid"),size=1)+
  labs(title = 
         "Performance comparision of various Indices b/w 1991-'99", 
       y = "Absolute Monetery value($)",x="Time")+
  theme(axis.line = element_line(colour = "black", size = 0.6, 
                                 linetype = "solid"), 
        axis.title.x = element_text(face="bold",size=13), 
        axis.title.y = element_text(face="bold",size=13),
        axis.text.x = element_text(face = "bold",size = 12),
        axis.text.y = element_text(face = "bold",size = 12)))
```

f) By analyzing the last graph(e), we get to know that, the SMI(Swiss Market Index) outperforms all the the other indices (DAX, CAC and FTSE) for almost the entire time-span given(1991-1999).
